\subsection{External Interface Requirements}
\subsubsection{User Interfaces}
\hspace{\parindent}The CLup application interface will have to serve two types of users: customers and store managers. Opening screen of the application allows the user to pick a store or to login as a store manager. Depending on the choice, another screen is presented. For a customer, a screen with the options to retrieve a ticket, book a visit or change the store. For a store manager, a screen containing their camera view, and buttons to confirm the scanned ticket, notify the system about a customer exit and to log out of the application. 
\subsubsection{Hardware Interfaces}
\hspace{\parindent}Depending on the current user the CLup application will require access to some hardware interfaces. If the current user is a customer, the application will require the device's camera and if the current user is the store manager the GPS location data will be needed. The application will require no further hardware interfaces.
\subsubsection{Software Interfaces}
\hspace{\parindent}The CLup application will not require any specific software interfaces.
\subsubsection{Communication Interfaces}
\hspace{\parindent}The most important communication will occur between the device and the database. The decision on the specific communication interface which will be used depends on the database, and is, therefore, left to the developers.

\newpage
\subsection{Functional Requirements}
\begin{enumerate}
	\item [\textbf{G1}] Allow a User to "line up"/retrieve a number.
	\begin{enumerate}
		\item [\textbf{G1.1}] Allow a User to retrieve a number through the application.
		\begin{enumerate}
			\item [\textbf{R1}] The user must be able to select a specific store in which they want to do the shopping.
			\item [\textbf{R2}] The user must be able to request a number and a ticket.
			\item [\textbf{R3}] The user must be able to receive a number and a ticket.
		\end{enumerate}
		\item [\textbf{G1.2}] Allow a User to retrieve a number physically from the printer.
		\begin{enumerate}
			\item [\textbf{R4}] The user must be able to physically retrieve a ticket from the printer containing a number and a QR code.		
		\end{enumerate}
		\item [\textbf{D8}] The user has internet connection for the device at all times.
	\end{enumerate}
	\item [\textbf{G2}] Allow a Store Manager to control the entrance of a User via QR code scanning.
	\begin{enumerate}
		\item [\textbf{R5}] The store manager must be able to scan a QR code.
		\item [\textbf{R6}] The store manager must be informed by the application if a user tries to enter the store out of order.
		\item [\textbf{R7}] The store manager must be informed when the capacity of the store is full.
		\item [\textbf{R8}] The store manager must be able to alert the system whenever a customer exits the store.
		\item [\textbf{D6}] The system can correctly save data about enter and exit times of anonymous customers, in order to calculate estimated wait time.
		\item [\textbf{D8}] The user has internet connection for the device at all times.
	\end{enumerate}
	\item [\textbf{G3}] Allow a User to get precise calculations of the wait time.
	\begin{enumerate}
		\item [\textbf{R9}] Allow the user to receive a precise estimation of wait time when retrieving a number.
		\item [\textbf{R10}] The system must provide the user with an estimation of wait time based on data.
		\item [\textbf{D4}] The system can use data about the registered user to calculate estimated wait time.
		\item [\textbf{D6}] The system can correctly save data about enter and exit times of anonymous customers, in order to calculate estimated wait time.
		\item [\textbf{D8}] The user has internet connection for the device at all times.
	\end{enumerate}
	\item [\textbf{G4}] Allow a User to get updates/notifications on the estimated wait time.
	\begin{enumerate}
		\item [\textbf{R11}] The system must be able to update its estimated wait time in real time.
		\item [\textbf{R12}] The system must be able to send an update to the user in specific intervals regarding estimated wait time until it's their turn.
		\item [\textbf{D4}] The system can use data about the registered user to calculate estimated wait time.
		\item [\textbf{D6}] The system can correctly save data about enter and exit times of anonymous customers, in order to calculate estimated wait time.
		\item [\textbf{D8}] The user has internet connection for the device at all times.
	\end{enumerate}
	\item [\textbf{G5}] Allow a User to "book a visit" to the store.
	\begin{enumerate}
		\item [\textbf{G5.1}] Allow a User to "book a visit" to the store without indicating the expected duration of the visit.
		\begin{enumerate}
			\item [\textbf{R13}] The user must be able to request to see all the available timeslots in that specific store.
			\item [\textbf{R14}] The system must be able to provide the user with the list of all available timeslots upon the request.
			\item [\textbf{R15}] The user must be able to select a specific timeslot.
			\item [\textbf{R16}] The user must be able to receive a confirmation of his timeslot reservation, along with a number and a ticket.
			\item [\textbf{R17}] Allow the user to be at most five minutes late for his reservation before canceling his ticket.
		\end{enumerate}
		\item [\textbf{G5.2}] Allow a User to "book a visit" to the store with indicating the expected duration of the visit.
		\begin{enumerate}
			\item [\textbf{R18}] The user must be able to specify expected duration of his visit to the store.
		\end{enumerate}
 		\item [\textbf{D3}] The user's device provides accurate GPS information.
		\item [\textbf{D7}] The system can correctly save data to and pull data from available time slot schema in the database. 
		\item [\textbf{D8}] The user has internet connection for the device at all times.
	\end{enumerate}
	\item [\textbf{G6}] Allow a Store Manager to login to his store manager account with credentials.
	\begin{enumerate}
		\item [\textbf{R19}] The store manager must be provided with the login credentials upon request to the system administrator.
		\item [\textbf{D1}] The store manager's username must be unique. 
		\item [\textbf{D2}] The store manager's password must be secure. 
	\end{enumerate}
\end{enumerate}

\newpage
\begin{table}[]
\centering
\begin{tabular}{|
>{\columncolor[HTML]{EFEFEF}}l |l|l|}
\hline
\cellcolor[HTML]{C0C0C0}\textbf{Requirement, {[}Rn{]}} & \cellcolor[HTML]{C0C0C0}\textbf{Goals, {[}Gn{]}} & \cellcolor[HTML]{C0C0C0}\textbf{Domains, {[}Dn{]}} \\ \hline
R1  & G1.1 & D8         \\ \hline
R2  & G1.1 & D8         \\ \hline
R3  & G1.1 & D8         \\ \hline
R4  & G1.2 & D8         \\ \hline
R5  & G2   & D6, D8     \\ \hline
R6  & G2   & D6, D8     \\ \hline
R7  & G2   & D6, D8     \\ \hline
R8  & G2   & D6, D8     \\ \hline
R9  & G3   & D4, D6, D8 \\ \hline
R10 & G3   & D4, D6, D8 \\ \hline
R11 & G4   & D4, D6, D8 \\ \hline
R12 & G4   & D4, D6, D8 \\ \hline
R13 & G5.1 & D3, D7, D8 \\ \hline
R14 & G5.1 & D3, D7, D8 \\ \hline
R15 & G5.1 & D3, D7, D8 \\ \hline
R16 & G5.1 & D3, D7, D8 \\ \hline
R17 & G5.1 & D3, D7, D8 \\ \hline
R18 & G5.2 & D3, D7, D8 \\ \hline
R19 & G6   & D1, D2     \\ \hline
\end{tabular}
\caption{Mapping table}
\label{tab:my-table}
\end{table}
\subsection{Performance Requirements}

